A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Figures

### 2021-07-31 writeUp/figures.tex
updated figure caption about ordering

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_individualEstimates_allSpecies_withoutBalabacensis.pdf}}
	\caption{\textbf{MRR: lifespan estimates for each time series.} The middle point shows the median estimates, and the left and right box whiskers show the 25\%, and 75\% posterior quantiles respectively. All estimates were obtained using the non-hierarchical exponential survival model as described in text.}
	\label{fig:mrr_lifespan_individualEstimates}
\end{figure}

>>>>

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_individualEstimates_allSpecies_withoutBalabacensis.pdf}}
	\caption{\textbf{MRR: lifespan estimates for each time series.} The middle point shows the median estimates, and the left and right box whiskers show the 25\%, and 75\% posterior quantiles respectively. All estimates were obtained using the non-hierarchical exponential survival model as described in text. The individual estimates within each species are ordered according to the median lifespan estimates; the species estimates are ordered corresponding to the species-level medians.}
	\label{fig:mrr_lifespan_individualEstimates}
\end{figure}
